%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------
\cventry
{Engineer Lead} % Job title
{Al toque QR} % Organization
{Remote, Tandil, Argentina} % Location
{Jul. 2024 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Hired and train a team of 2 jr devs, 1 mid-level and ux researcher}
\item {Prepare and do IRL interviews with clients and future users}
\item {Prepare weekly meetings with stakeholders to show progress and define directions}
\item {Monthly and Weekly planning using Linear}
\item {Design development and QA process}
\item {Setup CI/CD and deployments in Digital Ocean and Vercel}
\item {Build API with Express.js and PostgreSQL}
\item {Build React with Next.js}
\end{cvitems}
}
%------------------------------------------------
\cventry
{Developer} % Job title
{Brink Trade} % Organization
{Remote} % Location
{Mar. 2022 - May 2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Build a public API with public documentation from scratch. Using Node.js, Express.js \& Typescript}
\item {Stack: React, Express, PostgreSQL}
\item {Design PostgreSQL schema for Protocol contracts v2 and build an DB client}
\item {Build react functionality to track tx status on browser}
\item {Contributed with an indexer services, with a Solver/filler worker and with the SDK}
\item {Mentor on hackathon}
\end{cvitems}
}
%------------------------------------------------
\cventry
{Tech Lead} % Job title
{Proyecto DIDI} % Organization
{Buenos Aires, Argentina} % Location
{Jan. 2021 - Jul. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Hired and coordinated a team of 6 devs}
\item {Coordinate with 5 external teams}
\item {Design and QA flows for 5+ services and apps}
\item {Design new functionalities and interfaces between apps and services}
\item {Architecture evaluations and reviews}
\item {Team review and feedback}
\end{cvitems}
}
%------------------------------------------------
% \cventry
% {Solidity developer} % Job title
% {Freelance} % Organization
% {Remote} % Location
% {Aug. 2021} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Stack: Solidty, Hardhat}
% \item {Netowrks: Binance, Binance testnet, Ropsten testnet}
% \item {ERC-20, BEP-20 token}
% \end{cvitems}
% }
%------------------------------------------------
\cventry
{Consultant} % Job title
{Proyecto DIDI} % Organization
{Buenos Aires, Argentina} % Location
{Apr. 2020 - Dec. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Lead and review code from a few external companies building for us}
\item {System design internally and externally based on opposite stakeholders points of view}
\item {Manual QA of the entire stack}
\end{cvitems}
}
%------------------------------------------------
\cventry
{Core Developer} % Job title
{Windingtree} % Organization
{Remote} % Location
{Dec. 2019 - Feb. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Build an API to integrate travel services (Sabe, Airfrance, etc..). Transfor from XML/SOAP responses to JSON}
\end{cvitems}
}
%------------------------------------------------
\cventry
{Javascript Developer} % Job title
{Xoor} % Organization
{Mar del Plata, Argentina} % Location
{Mar. 2019 - Oct. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Build a GraphQL API, with PostgreSQL and deployed to AWS}
\item {Build REST API with express.js and using MongoDB }
\end{cvitems}
}
%------------------------------------------------
\cventry
{Developer} % Job title
{Windingtree} % Organization
{Remote} % Location
{Dec. 2017 - Jan. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Build API to access onchain smart contracts, IPFS data and index onchain events}
\item {Booking App for ETHBerlin 2018. Based on React, Express, Mongo and and BIP39 HDWallets}
\item {Contributed to Javascript sdk}
\item {Mentor on hackathon}
\end{cvitems}
}
%------------------------------------------------
\cventry
{JavaScript backend developer} % Job title
{Bons} % Organization
{Buenos. Aires., Argentina} % Location
{Jan. 2017 - Dec. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Build a microservices architecture using Seneca.js and Express.js}
\item {Build a REST API using Express.js }
\item {Created a cache layer for external services using Mongo and Redis}
\item {Fix React small bugs}
\end{cvitems}
}
%------------------------------------------------
\cventry
{SAP ABAP \& JavaScript Developer} % Job title
{Grupo Assa} % Organization
{Tandil, Argentina} % Location
{Mar. 2015 - Jan. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Stack: ABAP, JavaScript, Node, Linux}
\end{cvitems}
}
%------------------------------------------------
\end{cventries}
